Detecting strongly lensed quasars by pixel-level model comparison

### 2015-04-06 docs/paper1.tex

@@

>>>>

An alternative approach is explored in a paper by Chan et al (2014). These
authors investigate the greater execution speed achievable by first
extracting point source positions by ad-hoc means, and then fitting lens
models to these reduced data instead of the pixel values. They also pursue
the first method for assessing lens plausibility, focusing on the goodness
of fit of the lens models, and interpreting this in the context of a
training set. Comparison between the two approaches will help guide the
community as it approaches the wide field survey datasets of DES, HSC and
LSST.

@@

\subsection{Models: Lenses and Nebulae}
\label{sec:model:ln}

\subsection{Inference with The Tractor}
\label{sec:model:tractor}

\subsection{Model Comparison by Approximate Plausibility Ratio}
\label{sec:model:bic}
